%\documentclass[12pt]{article}
 \input{imports}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}

\begin{document}
\title{Final Project Setup}
\author{Yobin Timilsena \& Mitchell Valdes-Bobes}
\maketitle
% \begin{abstract}
% 	We examine [X]
% \end{abstract}
% \thispagestyle{empty}

% \pagebreak{}
% This paper .... 


\section{Model}
\begin{itemize}
	\item Households live for $ T $ periods, without retirement. Agents are heterogeneous in human capital $ h $ and assets $ k $. Agents are either employed or unemployed (but looking for a job). They spend $ s $ proportion of time in school each period.  Moreover, $ S $ represents cumulative years of schooling.
	There are two kinds of firms: a high type and a low type.
\end{itemize}

\subsection{Firms}
\begin{itemize}
    \item There are $2$ firm types $I \in \{L,H\}$, with $ \mu $ fraction of firms being the low type.
    \item Firm type $I=L$ hires all workers while firm type $I=H$ hires only workers with $S \geq \underline{S}$.
\end{itemize}

\subsection{Workers}
\begin{itemize}
    \item Law of motion of human capital is: $h' = \exp(z) H(h,s)$ where $z \in \mathbb{R}_+$ is a random shock. 
\end{itemize}
\subsubsection{Unemployed Workers}
\begin{itemize}
    \item Search for a job with intensity $\gamma$, $(\gamma + s = 1)$.
    \item Receive a job offer with probability $\pi(\gamma, S)$, $(\pi(0,\cdot) = 0)$ -- $ \pi_t(\gamma, S) = \gamma \cdot \frac{S}{t} $.
    \item Dependent on $S$ they might receive an offer from just $L$ or both firms.
    \item Receive unemployment benefits $b$ while unemployed.
    
    \item There are $3$ state variables:
    \begin{itemize}
    	\item $h \in \mathbb{R}_+$ human capital. Law of motion $ h' = \exp{z'} H(h,s) $.
    	\item $k \in \mathbb{R}_+$ assets.
    	\item $S \in \mathbb{R}_+$ (accumulated) schooling. Law of motion $ S' = S + s $.
    \end{itemize}
\end{itemize}

\textbf{Value Function if $S < \underline{S}$}

\begin{align*}
    U_t(h,k,S) =  \max_{k',s} \left\{ u(c) + \beta\mathbb{E}\left[\pi(\gamma, S) \cdot \mu \cdot W^L_{t+1}(h',k',S')
    + (1 - \pi(\gamma, S) \cdot \mu)U^L_{t+1}(h',k',S')  \right] \right\}
\end{align*}


\textbf{Value Function if $S \geq \underline{S}$}

\begin{align*}
	U_t(h,k,S) = &  \max_{k',s} \biggl\{ u(c) + \beta\mathbb{E}\biggl[\pi(\gamma, S) \left[\mu W^L_{t+1}(h',k',S') + (1 - \mu) W^H_{t+1}(h',k',S') \right]  \\
		+ & (1 - \pi(\gamma, S)) U^L_{t+1}(h',k',S')  \biggr] \biggr\}
\end{align*}
with the budget constraint \[  c + k' \leq b + k(1+r). \]

\subsubsection{Employed Workers}
\begin{itemize}
	\item Divide their time for $ s + l = 1 $.
	\item No on-the-job search allowed.
\end{itemize}

\textbf{Value function}
\begin{align*}
	W^I_t(h,k,S) =  \max_{k',s} \left\{ u(c) + \beta\mathbb{E}\left[ (1 - \delta) W^I_{t+1}(h',k',S')
	+ \delta  U_{t+1}(h',k',S')  \right] \right\}
\end{align*}
with the budget constraint \[   c + k' \leq R^I_t h l + k(1 +r) \]
% \begin{align*}
%     U_t(h,k,S) = \\
%     &\max_{k,s} \left\{ u(c) + \beta\mathbb{E}\left[\pi(\gamma, S)\left(\mu W^L_{t+1}(h',k',S')
%     + (1 - \pi(\gamma, S))U^L_{t+1}(h',k',S')  \right] \right\}
% \end{align*}




%\bibliographystyle{chicago}
%\bibliography{references}


\end{document}